---
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
set.seed(42)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bayefdr

<!-- badges: start -->
[![R build status](https://github.com/VallejosGroup/bayefdr/workflows/R-CMD-check/badge.svg)](https://github.com/VallejosGroup/bayefdr/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/bayefdr)](https://CRAN.R-project.org/package=bayefdr)
[![downloads](http://cranlogs.r-pkg.org/badges/grand-total/bayefdr)](http://CRAN.R-project.org/web/packages/bayefdr/index.html)
<!-- badges: end -->

The goal of bayefdr is to provide tools for the estimation and optimisation
of Bayesian expected false discovery and expected false negative rates.

## Installation

You can install the released version of bayefdr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bayefdr")
# development version:
## devtools::install_github("VallejosGroup/bayefdr")
```

## Usage

The main functions in this package are `efdr`, `efnr` and `efdr_search`.
`efdr` and `efnr` calculate the EFDR or EFNR for a vector of probabilities
given a specified probability threshold. `efdr_search` finds the probability
threshold that matches a target EFDR as closely as possible.
The basic input to this function is a vector of probabilities and a target EFDR.

```{r example}
library("bayefdr")
set.seed(42)
probs <- runif(100)
efdr(0.7, probs)
efnr(0.7, probs)
efdr <- efdr_search(probs, target_efdr = 0.1)
efdr
```

The output of this function is a `data.frame` with some extra attributes. There
is a plot method too.

```{r outputs}
head(efdr)
plot(efdr)
```
